2016 Brussels Bombings

### 2019-05-25 report/report.Rmd
Fix date time locale

```{r}
datatable(ufo[orig == bru, .(dest, airline, aircraft, takeoff, landing)], options = list(dom = 'tp', columnDefs = list(list(className = 'dt-center', targets = '_all'))), colnames = c('Destination', 'Airline', 'Aircraft', 'Departure', 'Arrival')) %>%
	formatDate(columns = c('takeoff', 'landing'), method = 'toLocaleString')
```

>>>>

```{r}
datatable(ufo[orig == bru, .(dest, airline, aircraft, takeoff, landing)], options = list(dom = 'tp', columnDefs = list(list(className = 'dt-center', targets = '_all'))), colnames = c('Destination', 'Airline', 'Aircraft', 'Departure', 'Arrival')) %>%
	formatDate(columns = c('takeoff', 'landing'), method = 'toLocaleString', params = list('ca-ES'))
```
